The Effects of weather on maize yield: New evidence from Kenya

### 2019-01-15 writing/draft4/draft22.tex
writing MAPE

\begin{center}
\begin{threeparttable}
\caption{\label{CV}	Leave-one-out cross validation: Mean absolute prediction error divided by IQR}
\linespread{1.3}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates\tnote{a}}&\textbf{Only seasonal\tnote{b}}&\textbf{Naive forecast\tnote{c}}\\
\hline
{All counties}&$0.3811$&$0.3889$&$0.4277$\\
{ASAL}&$0.5300$&$0.5342$&$0.5835$\\
{non-ASAL}&$0.3858$&$0.4043$&$0.4510$\\
\br
\end{tabular}
\end{indented}
 \begin{tablenotes}
  \begin{footnotesize}
  \item[a] Mixed effects models: the preferred specification with all fixed effects presented in table~\ref{MainEst}.
  \item[b] Mixed effects models: the baseline specification, only seasonal precipitation and average seasonal temperature in the fixed effects.
  \item[c] Last period's actual values used as this period's forecast.
  \end{footnotesize}
\end{tablenotes}
\end{threeparttable} 
\end{center}
\vspace{1cm}

\appendix
\section*{Appendix}

@@

\begin{center}
\begin{threeparttable}
\caption{\label{CV}	Leave-one-out cross validation: Mean absolute prediction error}
\linespread{1.3}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates\tnote{a}}&\textbf{Only seasonal\tnote{b}}&\textbf{Naive forecast\tnote{c}}\\
\hline
{All counties}&$0.3599$&$0.3673$&$0.4040$\\
{ASAL}&$0.4352$&$0.4385$&$0.4790$\\
{non-ASAL}&$0.2715$&$0.2845$&$0.3173$\\
\br
\end{tabular}
\end{indented}

 \begin{tablenotes}
  \begin{footnotesize}
  \item[a] Mixed effects models: the preferred specification with all fixed effects presented in table~\ref{MainEst}.
  \item[b] Mixed effects models: the baseline specification, only seasonal precipitation and average seasonal temperature in the fixed effects.
  \item[c] Last period's actual values used as this period's forecast.
  \end{footnotesize}
\end{tablenotes}
\end{threeparttable} 
\end{center}
\vspace{1cm}

>>>>

The scaled MAPE of our preferred specification and the two baseline predictions can be found in table~\ref{CVdiv}. All three predictions were obtained for the sample of all counties and also for the models based on the subsamples of ASAL and non-ASAL counties. The values of MAPE not divided by IQR can be found in table~\ref{CV} in the appendix.

\begin{center}
\begin{threeparttable}
\caption{\label{CVdiv}	Leave-one-out cross validation: Mean absolute prediction error divided by IQR}
\linespread{1.3}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample}&\textbf{Preferred specification\tnote{a}}&\textbf{Baseline specification\tnote{b}}&\textbf{Naive forecast\tnote{c}}\\
\hline
{All counties}&$0.3811$&$0.3889$&$0.4277$\\
{ASAL}&$0.5300$&$0.5342$&$0.5835$\\
{non-ASAL}&$0.3858$&$0.4043$&$0.4510$\\
\br
\end{tabular}
\end{indented}
 \begin{tablenotes}
  \begin{footnotesize}
  \item[a] Mixed effects models: the preferred specification with all fixed effects listed in table~\ref{MainEst}.
  \item[b] Mixed effects models: the baseline specification, only seasonal precipitation and average seasonal temperature in the fixed effects.
  \item[c] Last period's actual values used as this period's forecast.
  \end{footnotesize}
\end{tablenotes}
\end{threeparttable} 
\end{center}
\vspace{1cm}

According to MAPE, our preferred specifications perform better than the baseline mixed effects models and considerably better than the naive forecasts for all three samples (table~\ref{CVdiv}). For all three prediction methods, the smallest values of MAPE were achieved for the sample of all counties while the least precise forecasts with regard to MAPE were obtained for the subsample of ASAL counties (table~\ref{CVdiv}).

\clearpage
\section{Conclusions}\label{Conclusions}
\clearpage
\appendix
\section*{Appendix}

@@

\begin{center}
\begin{threeparttable}
\caption{\label{CV}	Leave-one-out cross validation: Mean absolute prediction error}
\linespread{1.3}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample}&\textbf{Preferred specification\tnote{a}}&\textbf{Baseline specification\tnote{b}}&\textbf{Naive forecast\tnote{c}}\\
\hline
{All counties}&$0.3599$&$0.3673$&$0.4040$\\
{ASAL}&$0.4352$&$0.4385$&$0.4790$\\
{non-ASAL}&$0.2715$&$0.2845$&$0.3173$\\
\br
\end{tabular}
\end{indented}

 \begin{tablenotes}
  \begin{footnotesize}
  \item[a] Mixed effects models: the preferred specification with all fixed effects listed in table~\ref{MainEst}.
  \item[b] Mixed effects models: the baseline specification, only seasonal precipitation and average seasonal temperature in the fixed effects.
  \item[c] Last period's actual values used as this period's forecast.
  \end{footnotesize}
\end{tablenotes}
\end{threeparttable} 
\end{center}
\vspace{1cm}
